---
title: "iTrack COVID - Canada"
# date: "(`r format(Sys.time(), '%d %B, %Y')`)"
# author: Dmitry Gorodnichy
output: 
  flexdashboard::flex_dashboard:
    # theme: simplex # journal # theme: simplex
    orientation: rows
    social: menu
    # source_code: embed
    vertical_layout: fill #scroll #fill
    logo: covid-48.png
    favicon: covid-48.png 
    navbar: 
      - { title: "Canada", href: "https://itrack.shinyapps.io/covid?region=Canada&N=50&national=0", align: right }
      - { title: "US", href: "https://itrack.shinyapps.io/covid?region=US&N=50&national=0#section-map", align: right }
      - { title: "Europe", href: "https://itrack.shinyapps.io/covid?region=Europe&N=50&national=1#section-map", align: right }
runtime: shiny       
---


```{r readData, include=FALSE}

# setwd("/home/dmitry/GitHub/iTrack-covid-priv")
source("covid-read.R")


STR_ALL <- "[ All ]"
STR_TOTAL <- "[Show Total]"

if (F) {
  input <- list()
  #input$date <- dtJHU$date %>% max
  input$country <- "Canada"
  input$state <- "(National)"
  input$state <- "Ontario"
  input$city <- "Ottawa"
  input$f = "Speed"
  input$normalize = T
  input$convolution = 7
}


```

```{r readCanada, include=F}


strCovid <- "https://docs.google.com/spreadsheets/d/1D6okqtBS3S2NRC7GFVHzaZ67DuTw7LX49-fqSLwJyeo/"
sheets <- c("Cases" ,"Mortality" ,"Recovered", "Testing" ,"Codebook")


fOpen <- function(i, col1name) {
  strCovidCsv <- paste0(strCovid, "gviz/tq?tqx=out:csv&sheet=", sheets[i])
  dt <- fread(strCovidCsv, header=T, select= 1:15, stringsAsFactors = F)
  setnames (dt, c(col1name, names (dt) [-1] ) )
  return(dt)
}

fRemoveV <- function(dt) {
  str <- names(dt)
  cols <- str [ str_detect(str, regex("^V+")) ]
  dt [ , (cols):=NULL ]
  print(str)
  return(dt)
}

dtCases <<- fOpen(1, "case_id")  %>% fRemoveV() %>%  lazy_dt() %>% select(1:12) %>% as.dt() 
dtMortality  <<- fOpen(2,"death_id") %>% fRemoveV() %>%  lazy_dt() %>% select(c(1:9, 11)) %>%  as.dt()
dtRecovered  <<- fOpen(3,"date_recovered") %>% fRemoveV() %>%  lazy_dt() %>% select(1:4) %>% as.dt()
dtTesting  <<- fOpen(4,"date_testing") %>% fRemoveV() %>%  lazy_dt() %>% select(1:4) %>% as.dt()


setnames(dtCases, "date_report", "date")
setnames(dtMortality, "date_death_report", "date")
setnames(dtRecovered, "date_recovered", "date")
setnames(dtTesting, "date_testing", "date")

setnames(dtCases, "health_region", "city")
setnames(dtMortality, "health_region", "city")

setnames(dtCases, "province", "state")
setnames(dtMortality, "province", "state")
setnames(dtRecovered, "province", "state")
setnames(dtTesting, "province", "state")


dtCases [ , date := dmy(date)]
dtMortality [ , date := dmy(date)]
dtRecovered [ , date := dmy(date)]
dtTesting [ , date := dmy(date)]

# # # . state level ----

dtDailyCasesTotals <- dtCases[ , .(cases=.N), keyby = c("date", "state")]; dtDailyCasesTotals$type="confirmed"
dtDailyMortTotals  <- dtMortality[ , .(cases=.N), keyby = c("date", "state")]; dtDailyMortTotals$type="death"
dtRecoveredTotals  <- dtRecovered[ , .(cases=.N), keyby = c("date", "state")]; dtRecoveredTotals$type="recovered"

dt <- dtDailyCasesTotals %>% rbind (dtDailyMortTotals) %>% rbind(dtRecoveredTotals)
dt$country="Canada"
dt$city="[Provincial Total]"
setkey(dt, date, country, state, city,type)

dt0 <- dcast(dt, date+country+state+city ~ type, value.var="cases")
setcolorder(dt0,  c("date",  "country","state", "city",  "confirmed","death",  "recovered") )

# . city level ####

dtDailyCasesTotals <- dtCases[ , .(cases=.N), keyby = c("date", "state", "city")]; dtDailyCasesTotals$type <- "confirmed"
dtDailyMortTotals  <- dtMortality[ , .(cases=.N), keyby = c("date", "state", "city")]; dtDailyMortTotals$type="death"

dt <- dtDailyCasesTotals %>% rbind (dtDailyMortTotals)
dt$country="Canada"
setkey(dt, date, country, state, city, type)


dt00 <- dcast(dt, date+country+state+city ~ type, value.var="cases")
dt00$recovered = NA

# DT::datatable(dtAll)

setcolorder(dt00,  c("date",  "country", "state",  "city", "confirmed","death",  "recovered") )

dtAll <<- dt0 %>% rbind(dt00)

colsGeo <- c("country",   "state",       "city")
dtAll[, (colsGeo):=lapply(.SD, iconv, to="ASCII//TRANSLIT"), .SDcols=colsGeo]

dtAll[, region:=paste0(str_trunc(state, 3, ellipsis = ""), ": ", city)]
dtAll




dtAll [, active := confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)]

dtAll[is.na(confirmed)]

colMetrics <<- c("confirmed","death",  "recovered", "active")
colGroups <<- c( "country", "city", "state")

dtAll [, (colMetrics):= lapply(.SD, tidyr::replace_na, 0), .SDcol = colMetrics]

dateMax <<- dtAll[confirmed>0]$date %>% max; dateMax
dateMin <<- dtAll[confirmed>0]$date %>% min; dateMin
datePlotFrom <- ymd("2020-03-12")

addDerivatives(dtAll, colMetrics, colGroups) #, input$convolution)



```




# Make selection: {.sidebar}


```{r selectInput}

# h4("Step 1: Analyze Risks")

# selectInput('country',
#             h5(paste0 ("Select Country (out of ", dtAll$country %>% unique %>% length, "):") ),
#             multiple=F,
#             selected = "Canada",
#             choices = c(
#               #STR_ALL,
#               dtAll$country %>% unique  )
# )
# 

r.dt0  <- reactive({
  dtAll
  # dtAll[ country %in% input$country]
})

renderUI({
  selectInput('state',
              # paste0 ("Select Provinces (out of ", r.dt0()$state %>% unique %>% length - 1, "):"),
              h5(paste0 ("Add Provinces (Press DEL to delete):")),
              multiple=T, 
              # selected = STR_ALL,
             # selected = c("Ontario", "Quebec"), 
             selected = c("Ontario"),
              choices = c(STR_ALL, r.dt0()$state %>% unique %>% sort() )  )
})

r.dt00  <- reactive({
  # r.dt0()[ state %in% input$state ]
  if (STR_ALL %in% input$state)
    r.dt0()
  else
    r.dt0()[ state %in% input$state ]
  
})

renderUI({
  selectInput('city',
              h5(paste0 ("Add Health Regions (out of ", r.dt00()$city %>% unique %>% length - 1, "):") ),
              multiple=T,
              selected = STR_ALL,
              # selected = c("Ont: Ottawa",
              #              # "Que: Capitale-Nationale", 
              #              "Ont: Toronto", 
              #              "Que: Outaouais", 
              #              "Que: Montreal"),
              # selected = STR_ALL
              choices = c(STR_ALL, r.dt00()$region %>% unique %>% sort() )  )
})

hr()
# h4("Step 2: Visualize Results")

# checkboxInput("normalize", "Normalize (per Million)", T)
checkboxInput("scale", "Keep the same scale", F)


checkboxInput("log10", "Use Log scale", F)

radioButtons("sortby", 
             "Sort results:",
             # "Search and sort criteria:",
             # "Sort results:",
               choices=c("From most to least infected " = "confirmedTotal",
                 "From fastest to slowest spreading" = "confirmedSpeed",
                 "From fastest to slowest accelerating" = "confirmedAccel.",
                 "From highest to lowest growth rate" = "confirmedGrowth",
                 "Alphabetically" = "region"),
             selected = "confirmedSpeed",
             inline=F)


hr()
radioButtons("fRadio", "Show: ", # Metric Functional:", # "f", "Functionals:", Show Compute
             c(
               # "Raw data (records/day)" = "",
               "Total infected" = "Total",
               "Speed (new cases a day)" = "Speed",
               "Acceleration (change in speed)" = "Accel.",
               # "Growth: N/N'" = "Growth0",
               "Growth rate (R0)" = "Growth."
             ), inline=F,
             selected = "Speed"
)


checkboxInput("provincial", "Include provincial totals", F)
#

# 
# 
# renderUI({
#   sliderInput("showN", "Limit number of results to:", 
#               min = 1, max = r.dt00()$city %>% unique %>% length - 1, 
#               post  = " regions",
#               value = 15)
# })
# 
# 


hr()


sliderInput("convolution", "Adjust precision:", #"Convolution filter size", # "Compute over:", #Averaging  window size, #Precision
            min = 2, max = 10, post  = " days",
            value = 5)


# h4("Step 3: Model and Forecast ")

checkboxInput("trend", "Overlay model", T)
# checkboxInput("predict", "Show predictions (COMING SOON)", F)

hr()


# sliderInput("daysToTrack", label = "Days to track:",
            # min = 7, max = 120, value=60)

dateInput("date",
          label = h5("Adjust starting date:"), weekstart=1,
          min = "2020-03-01",
          max= format(Sys.time(), "%Y-%m-%d"),
          value = "2020-04-25"  # format(Sys.time(), "%Y-%m-%d") # "%d %B, %Y")`
)


r.dt000  <- reactive({
  if (STR_ALL %in% input$city )        
    dt000 <- r.dt00() 
  else
    dt000 <- r.dt00()[ region %in% input$city ]  
  
  # dt000 <- r.dt00()[ city %in% input$city ] 
  # dt000 <- r.dt00()
  
  if (!input$provincial)
    dt000 <- dt000[city!="[Provincial Total]"]
  
  # 
  #   setkey(dt000, input$sort)
  #     dt000 <- dt000[1:input$sortN] 
  
  dt000 <- dt000[ date >= input$date]
  
  colMetrics <<- c("confirmed","death",  "recovered", "active")
  colGroups <<- c( "country", "city", "state")
  addDerivatives(dt000, colMetrics, colGroups,input$convolution)
  
  dt000
  
  dt000 [ , deathRate:= as.integer(deathTotal / confirmedTotal * 100 )]
  dt000 [ , recoveryRate:= as.integer(recoveredTotal / confirmedTotal * 100 )]
  dt000 [ , activeTotal.:= confirmedTotal - recoveredTotal - deathTotal]
  
})


r.dt000cols  <- reactive({
  
  
  r.dt000() [date==dateMax |    date==dateMax-1 |    date==dateMax-7 |  date==dateMax-30 ]  [
    , .(region, date,
        confirmedTotal, confirmedSpeed, confirmedAccel., confirmedGrowth., 
        activeTotal, 
        deathRate,  recoveryRate
    )] [order(region)]
  

  
})



# hr()


# # checkboxInput("recovered", "Include recovered statistics", F)
# # checkboxInput("death", "Include death statistics", F)
# checkboxInput("recovered", "Show recovery rate", F)
# checkboxInput("death", "Show death rate", F)


```

```{r r.dt00, include = F}

# See in select

```

---

 Data is loaded  from the [University of Toronto Coronavirus database](https://art-bd.shinyapps.io/covid19canada/). It was last updated on  `r dtAll$date %>% max %>% format("%d %B, %Y")`. To reload the data, press [here](https://itrack.shinyapps.io/covid/).



# Trends and Models


## .... Upper Row {data-height=830 .tabset .tabset-fade }


<!-- ##### \ \ Data is loaded  from [UoT Database](https://art-bd.shinyapps.io/covid19canada/). This database  was last updated on  `r dtAll$date %>% max %>% format("%d %B, %Y")`. To reload data, press [here](https://itrack.shinyapps.io/covid/). -->

<!-- ### New -->

<!-- ```{r} -->
<!-- r.gConfirmed <-  reactive({ -->

<!--     g <- plotTrends(dt00, input) -->


<!-- }) -->

<!-- renderPlot( { -->
<!--   print( r.gConfirmed() ) -->
<!-- }) -->
<!-- ``` -->

<!-- ###  Plot (for printing) -->

### Pandemic spread analysis

```{r}

r.g <-  reactive({
  
  cols <- c("confirmed", "recovered", "deaths", "active")
  cols3 <- paste0(cols, input$fRadio)
  
  
  # dt00 <<- r.dt00()[confirmed>0][date>ymd("2020-03-10")]
  dt00 <<- r.dt000()
  
  setcolorder(dt00, "date")
  
  # 
  # if (input$normalize == T)
  #   dt00[ , (cols3):= lapply(.SD, function(x) {as.integer(x/population*1000000)}),.SDcols=cols3]
  # 
  
  if (  dt00$region %>% unique %>% length > 0) {
    g <- ggplot( dt00  ) +

      facet_wrap(.~
                   # region
                   reorder(region, -get(input$sortby))
                 ,  
                 scales=ifelse(input$scale, "fixed", "free_y")   
      ) +
      # scale_y_continuous(limits = c(0.5, NA)) +
      scale_y_continuous(limits = c(min(dt00[[ cols3[1] ]]), NA )) +

      
      scale_x_date(
        # limits = c( NA, as.Date(dateMax + 3 )),  
        
        date_breaks = "1 week",
                   # date_minor_breaks = "1 day", 
                   date_labels = "%b %d") +
      

      geom_vline(xintercept=dateMax, col = "orange", size=2) +
      geom_vline(xintercept=dateMax-14, col = "orange", size=1) +
      geom_point(aes_string("date", cols3[1]), alpha=0.5, col="purple", size=2) +
      geom_line(aes_string("date", cols3[1]), alpha=0.5, col="purple", size=1) +
      
      
      
      theme_bw() +

      labs(
        #title=paste0("Pandemic situation in ", input$state), # ": Historical vs. Predicted"),
        subtitle=paste0(
          "", my.paste(input$state, ", "), ".  ",
          "Last updated: ", dateMax ), # ": Historical vs. Predicted"),
        #  title=paste0("", input$country), # ": Historical vs. Predicted"),
        # subtitle= "The number of Confirmed, Recovered, Death cases",
        title= paste0("Infected ", input$fRadio, " over time"),
        caption=paste0("Generated on ",  format(Sys.time(), "%d %B, %Y") ," by iTrack Covid (https://itrack.shinyapps.io/covid)"),
        #subtitle=paste0("Dates: ", dtJHU$date %>% min, " - ", dtJHU$date %>% max),
        # y=paste("Cases", input$fRadio, ifelse(input$normalize, " (per Million)","")),
        y=paste("Cases"),
        x=NULL
      )
    
    if (input$log10 ) {
      g <- g + scale_y_log10()
    }
    
    
    if (input$trend ) {
      
      # if (input$trend_SE ) {
      g <- g + geom_smooth(aes_string("date", cols3[1]), size = 1, level=0.99,
                           method= "gam", # method= "gam",  formula = y ~ s(x,k=3),
                           # method = "lm", formula = y ~ poly(x, 4),
                           col = "black", linetype = 2, alpha=0.5)
      # } else
      #   {
      #   g <- g + geom_smooth(aes_string("date", cols3[1]), size = 1, se = FALSE,
      #                        method= "gam",   # method= "gam",  formula = y ~ s(x,k=3),
      #                        # method = "lm", formula = y ~ poly(x, 4),
      #                        col = "black", linetype = 3, alpha=0.5)
      # }
      
    }  else {
      
      g <- ggplot () +  theme_bw() +
        
        annotate("text", x = 1, y = 3, label=paste0(
          "While data is being loaded ... \n\n", 
          "Tip of the Day: \n Bookmark this page on your phone to have live pandemic update in your pocket.\n\n"
          # ,
          # "Quote of the day: \n 'Happiness is not something ready made. It comes from your own actions' (Dalai Lama)"
        ) ) +
        annotate("text", x = 1, y = 1, label="") + 
        annotate("text", x = 1, y = 4, label="") + 
        labs(x=NULL, y=NULL)
      
    }
  }
  
})

renderPlot( {
  print( r.g() )
})
```


<!-- ###  Plot (Interactive) -->

<!-- ```{r} -->

<!-- renderPlotly( { -->
<!--   ggplotly(r.g()) -->
<!-- }) -->


<!-- ``` -->

# Table


## .... Upper Row {data-height=830 .tabset .tabset-fade }


<!-- ### Searchable table -->

### Detailed Results


```{r}

DT::renderDataTable({
  
  DT::datatable( r.dt000cols(),
                 filter ="top",
                 # colnames = c("Country", "Confirmed", "Recovered", "Death"),
                 options = list(
                   
                   searchHighlight = TRUE,
                   scrollX = TRUE,
                   #scrollX='400px',
                   scrollY = TRUE,
                   bPaginate = T,
                   pageLength = 10)
  )
})

```


### Printable table 
```{r}

renderPrint({
  
  r.dt000cols() %>% knitr::kable()
})

```



###  Printable table (alternative view)

```{r}

renderTable({
  r.dt000cols() 
  })

```



```{r covid.9.help.Rmd, child = 'covid.9.help.Rmd'}
```

