---
title: "iTrack COVID: Canada"
# author: Dmitry Gorodnichy (www.gorodnichy.ca)
output: 
  flexdashboard::flex_dashboard:
    # theme: simplex # journal # theme: simplex
    orientation: rows #columns #rows
    social: menu
    # source_code: embed
    vertical_layout: fill #scroll #fill
    logo: covid-48.png
    favicon: covid-48.png 
    navbar: 
      # - { title: "Ottawa (via API)", href: "?province=Ontario&city=Ottawa", align: right }
      # - { title: "Ontario (via API)", href: "https://itrack.shinyapps.io/covid/ca.Rmd?province=Ontario", align: right }
      - { title: "US", href: "https://itrack.shinyapps.io/covid/us.Rmd", align: right }
      - { title: "World", href: "https://itrack.shinyapps.io/covid?region=Europe&N=50&national=1#section-map", align: right }
runtime: shiny       
---


```{r readData, include=FALSE}

source("covid-functions.R")

if (F) { # input <- list() ----
  input <- list()
  input$sortby <- "confirmedSpeed"
  #input$date <- dtJHU$date %>% max
  input$country <- "Canada"
  input$state <- "Ontario"
  input$city <- "Ottawa"
  input$f = "Speed"
  input$normalize = T
  input$convolution = 7
  input$daysToTrack = 8 # weeks
  input$scale = F
  input$log10 = F
  input$trend = T
}


```

```{r readCanada, include=F}

if (T) {
  strCovid <- "https://docs.google.com/spreadsheets/d/1D6okqtBS3S2NRC7GFVHzaZ67DuTw7LX49-fqSLwJyeo/"
  sheets <- c("Cases" ,"Mortality" ,"Recovered", "Testing" ,"Codebook")
  
  
  fOpen <- function(i, col1name) {
    strCovidCsv <- paste0(strCovid, "gviz/tq?tqx=out:csv&sheet=", sheets[i])
    dt <- fread(strCovidCsv, header=T, select= 1:15, stringsAsFactors = F)
    setnames (dt, c(col1name, names (dt) [-1] ) )
    return(dt)
  }
  
  fRemoveV <- function(dt) {
    str <- names(dt)
    cols <- str [ str_detect(str, regex("^V+")) ]
    dt [ , (cols):=NULL ]
    print(str)
    return(dt)
  }
  
  dtCases <<- fOpen(1, "case_id")  %>% fRemoveV() %>%  lazy_dt() %>% select(1:12) %>% as.dt() 
  dtMortality  <<- fOpen(2,"death_id") %>% fRemoveV() %>%  lazy_dt() %>% select(c(1:9, 11)) %>%  as.dt()
  dtRecovered  <<- fOpen(3,"date_recovered") %>% fRemoveV() %>%  lazy_dt() %>% select(1:4) %>% as.dt()
  dtTesting  <<- fOpen(4,"date_testing") %>% fRemoveV() %>%  lazy_dt() %>% select(1:4) %>% as.dt()
  
  
  setnames(dtCases, "date_report", "date")
  setnames(dtMortality, "date_death_report", "date")
  setnames(dtRecovered, "date_recovered", "date")
  setnames(dtTesting, "date_testing", "date")
  
  setnames(dtCases, "health_region", "city")
  setnames(dtMortality, "health_region", "city")
  
  setnames(dtCases, "province", "state")
  setnames(dtMortality, "province", "state")
  setnames(dtRecovered, "province", "state")
  setnames(dtTesting, "province", "state")
  
  
  dtCases [ , date := dmy(date)]
  dtMortality [ , date := dmy(date)]
  dtRecovered [ , date := dmy(date)]
  dtTesting [ , date := dmy(date)]
  
  # # # . state level ----
  
  dtDailyCasesTotals <- dtCases[ , .(cases=.N), keyby = c("date", "state")]; dtDailyCasesTotals$type="confirmed"
  dtDailyMortTotals  <- dtMortality[ , .(cases=.N), keyby = c("date", "state")]; dtDailyMortTotals$type="death"
  dtRecoveredTotals  <- dtRecovered[ , .(cases=.N), keyby = c("date", "state")]; dtRecoveredTotals$type="recovered"
  
  dt <- dtDailyCasesTotals %>% rbind (dtDailyMortTotals) %>% rbind(dtRecoveredTotals)
  dt$country="Canada"
  dt$city="[Provincial Total]"
  setkey(dt, date, country, state, city,type)
  
  dt0 <- dcast(dt, date+country+state+city ~ type, value.var="cases")
  setcolorder(dt0,  c("date",  "country","state", "city",  "confirmed","death",  "recovered") )
  
  # . city level ####
  
  dtDailyCasesTotals <- dtCases[ , .(cases=.N), keyby = c("date", "state", "city")]; dtDailyCasesTotals$type <- "confirmed"
  dtDailyMortTotals  <- dtMortality[ , .(cases=.N), keyby = c("date", "state", "city")]; dtDailyMortTotals$type="death"
  
  dt <- dtDailyCasesTotals %>% rbind (dtDailyMortTotals)
  dt$country="Canada"
  setkey(dt, date, country, state, city, type)
  
  
  dt00 <- dcast(dt, date+country+state+city ~ type, value.var="cases")
  dt00$recovered = NA
  
  # DT::datatable(dtAll)
  
  setcolorder(dt00,  c("date",  "country", "state",  "city", "confirmed","death",  "recovered") )
  
  dtAll <<- dt0 %>% rbind(dt00)
  
  
  
  colsGeo <- c("country",   "state",       "city")
  dtAll[, (colsGeo):=lapply(.SD, iconv, to="ASCII//TRANSLIT"), .SDcols=colsGeo]
  
  dtAll[, region:=paste0(str_trunc(state, 3, ellipsis = ""), ": ", city)]
  dtAll
  
  
  
  dtAll [, active := confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)]
  dtAll[is.na(confirmed)]
  
  colMetrics <<- c("confirmed","death",  "recovered", "active")
  colGroups <<- c( "country", "city", "state")
  
  dtAll [, (colMetrics):= lapply(.SD, tidyr::replace_na, 0), .SDcol = colMetrics]
} else { # readCovidUofT () ----
  dtAll <- readCovidUofT ()
}


dateMax <<- dtAll[confirmed>0]$date %>% max; dateMax
dateMin <<- dtAll[confirmed>0]$date %>% min; dateMin
dateToday <- format(Sys.time(), '%d %B, %Y') %>% dmy; dateToday


# datePlotFrom <- ymd("2020-03-12")

addDerivatives(dtAll, colMetrics, colGroups) #, input$convolution)

# .................................... -------------

```


# Today
<!-- # Mobile view -->
<!-- # Automated search -->
<!-- # Daily Summary -->
<!-- # Summary and Trends -->
<!-- # Trends and Models -->
<!-- # Results -->
<!-- # Search results -->




## Search criteria: {.sidebar}



<!-- ## Make selection: {.sidebar} -->


<font size=-2> 

<!-- Please wait until the data is loaded from [University of Toronto Coronavirus database](https://github.com/ishaberry/Covid19Canada) and [Government of Canada site](https://www.canada.ca/en/public-health/services/diseases/coronavirus-disease-covid-19/epidemiological-economic-research-data.html). -->

Thank you for using the [iTrack COVID App](https://itrack.shinyapps.io/covid/), Canadian Edition.  This App provides LIVE updates on the situation with COVID-19 in Canada at the municipal level. The unique feature of the App is a fully automated *data science driven* approach for searching  and identifying high-risk regions in the country.  In addition, to searching by Total and New Cases, you can also search by *Acceleration*, which is change in new cases a day, and  *Growth Rate*, also known as *Reproduction Rate* or *Rt*.

<!-- This App provides LIVE updates on the situation with COVID-19 in Canada at the municipal level and enables automated search of high-risk areas in the country, sorted by pandemic Speed (new cases a day) and Growth  (also known as Reproduction Rate or Rt).  -->
<!-- You can  modify search criteria and display options in [Settings].  -->
<!-- Please see [Public Health of  Ontario page](https://www.publichealthontario.ca/-/media/documents/ncov/epi/covid-19-epi-evolution-case-growth-ontario.pdf?la=en) and [Official Government of Canada site](https://www.canada.ca/en/public-health/services/diseases/coronavirus-disease-covid-19/epidemiological-economic-research-data.html) for official data and explanation of the concepts visualized in this App. -->

<!-- The data is loaded from -->
<!-- [University of Toronto Coronavirus database](https://github.com/ishaberry/Covid19Canada), which was last updated on  `r dtAll$date %>% max %>% format("%d %B, %Y")`. If it takes too long to load the data, please try a few minutes later.   -->
<!-- Their server could be overloaded. -->

<!-- To reload data, press [here](https://itrack.shinyapps.io/covid/). -->
<!-- To start the search, please choose search region and criteria, then wait until the data is loaded from databases. -->
<!-- For official information about COVID-19 virus in Canada, please visit [Government of Canada site](https://www.canada.ca/en/public-health/services/diseases/coronavirus-disease-covid-19/epidemiological-economic-research-data.html). -->

<!-- https://doodles.mountainmath.ca/blog/2020/05/27/on-mixing-covid-19-and-census-data/ -->
<!-- https://doodles.mountainmath.ca/blog/2020/05/13/covid-19-data-in-canada-effective-reproduction-rates/ -->

<!-- https://resources-covid19canada.hub.arcgis.com/pages/open-data -->





</font>

<!-- ### Search criteria -->

```{r selectInput}


# https://github.com/daattali/advanced-shiny/blob/master/url-inputs/app.R
# observe({  ----

observe({
  query <- parseQueryString(session$clientData$url_search)
  if (!is.null(query[['province']])) {
    updateTextInput(session, "state", value = query[['province']])
  }    
  if (!is.null(query[['city']])) {
    updateTextInput(session, "city", value = query[['city']])
  }
  # if (!is.null(query[['N']])) {
  #   updateNumericInput(session, "showN", value = query[['N']])
  # } 
  if (!is.null(query[['sortby']])) {
    updateTextInput(session, "sortby", value = query[['sortby']])
  } 
})


# renderUI({
selectInput('state',
            # paste0 ("Select Provinces (out of ", r.dt0()$state %>% unique %>% length - 1, "):"),
            # h5(paste0 ("Select Provinces (Press DEL to delete):")),
            h5(paste0 ("Select Provinces (Leave blank to search entire country):")),
            width="100%",
            multiple=T, 
            # selected = STR_ALL,
            selected = c("Ontario", "Quebec"),
            # selected = c("Ontario"),
            # choices = c(r.dt0()$state %>% unique %>% sort() )  )
            choices = c(dtAll$state %>% unique %>% sort() )  )
# choices = c(STR_ALL, r.dt0()$state %>% unique %>% sort() )  )
# })


# renderUI({
selectInput('city',
            h5(paste0 ("Select City (Leave blank to search entire province):") ),
            width="100%",
            # h5(paste0 ("Select Health Regions (out of ", r.dt00()$city %>% unique %>% length - 1, ". Leave blank to search entire province):") ),
            # h5(paste0 ("Select Health Regions (out of ", r.dt00()$city %>% unique %>% length - 1, "):") ),
            multiple=T,
            # selected = STR_ALL,
            # selected = c("Ont: Ottawa",
            #              # "Que: Capitale-Nationale",
            #              "Ont: Toronto",
            #              "Que: Outaouais",
            #              "Que: Montreal"),
            # selected = STR_ALL
            # choices = c(STR_ALL, r.dt00()$region %>% unique %>% sort() )  )
            choices = c(dtAll$city %>% unique %>% sort() )  )
# choices = c(r.dt00()$region %>% unique %>% sort() )  )
# })

# 


checkboxInput("provincial", "Include provincial totals", F)


checkboxInput("overlaytext", "Overlay text", T)



# radioButtons("sortby",
#              "Sort results:",
#              # "Search and sort criteria:",
#              # "Sort results:",
#              choices=c("From most to least infected Total (Total confirmed cases)" = "confirmedTotal",
#                        "From fastest to slowest spread Speed (Average new cases a day)" = "confirmedSpeed",
#                        "From fastest to slowest spread Acceleration (Change in new cases a day)" = "confirmedAccel.",
#                        "From highest to lowest Growth rate (new cases today vs. new cases yesterday): Rt" = "confirmedGrowth." #,
#                        # "Alphabetically" = "region"
#                        ),
#              selected = "confirmedSpeed",
#              inline=F)

# radioButtons("sortby", 
#              h5("Sort results by :"),
#              # "Search and sort criteria:",
#              # "Sort results:",
#              choices=c("Total (Total number of confirmed cases): N(t)" = "confirmedTotal",
#                        "Speed (Average number of new cases a day): N'(t) = N(t)-N(t-1) " = "confirmedSpeed",
#                        "Acceleration (Change in number of new cases a day): N''(t) = N'(t)-N'(t-1)" = "confirmedAccel.",
#                        "Growth rate (Reproduction rate): R(t) = N'(t) / N'(t-1)" = "confirmedGrowth." #,
#                        # "Alphabetically" = "region"
#                        ),
#              selected = "confirmedSpeed",
#              inline=F)

radioButtons("sortby",
             h5("Search by :"),
             width="100%",
             # "Search and sort criteria:",
             # "Sort results:",
             choices=c(
               # "Total number of confirmed cases" = "confirmedTotal",
               # "Average number of new cases a day (Speed) " = "confirmedSpeed",
               # "Change in number of new cases a day (Acceleration)" = "confirmedAccel.",     
               "Total confirmed cases" = "confirmedTotal",
               "New cases a day (Speed) " = "confirmedSpeed",
               "Change in new cases a day (Acceleration)" = "confirmedAccel.",
               "Growth rate (Rt)" = "confirmedGrowth.", #,
               # "Alphabetically" = "region"
               "Name" = "region"
             ),
             selected = "confirmedSpeed",
             # selected = "region",
             inline=F)


# radioButtons("sortby2",
#              h5("Sort by :"),
#               width="100%",    
#              choices=c("Result", "Name",  "Location"),
#              selected = "Result",
#              inline=F)



sliderInput("showN",
            h5("Limit output to: "),
            min = 1, max = 100,
            # width="100%",
            # pre = "top search",
            step = 1,
            post  = " top results",
            # post  = " most infected regions",
            # value = min (r.dt00()$city %>% unique %>% length, 12))
            value = 30)




```



```{r r.dt, include=FALSE}
# r.dt0, r.dt00, r.dt000  ----


r.dt0  <- reactive({
  dtAll[date<=input$dateToday]
  # dtAll[ country %in% input$country]
})

r.dt00  <- reactive({
  
  my.state=input$state 
  
  # r.dt0()[ state %in% input$state ]
  if (is.null(my.state)) {
    # if (STR_ALL %in% input$state) {
    r.dt0()
  }  else
    r.dt0()[ state %in% my.state]
  
})


r.dt000  <- reactive({
  # dt000 <- dtAll[ city %in% my.city] 
  
  my.city <- input$city
  if (is.null(my.city)) {
    # if (STR_ALL %in% input$city )     {   
    dt000 <- r.dt00() 
  } else {
    dt000 <- r.dt00()[ city %in% my.city]
    # dt000 <- r.dt00()[ region %in% input$city ]
  }
  
  
  
  if (!input$provincial)
    dt000 <- dt000[city!="[Provincial Total]"]
  
  # 
  #   setkey(dt000, input$sort)
  #     dt000 <- dt000[1:input$sortN] 
  
  dt000 <- dt000[ date >= dateMax - input$daysToTrack*7 ] #input$date]
  
  colMetrics <<- c("confirmed","death",  "recovered", "active")
  colGroups <<- c( "country", "city", "state")
  
  addDerivatives(dt000, colMetrics, colGroups, input$convolution-1)
  
  dt000
  
  dt000 [ , deathRate:= as.integer(deathTotal / confirmedTotal * 100 )]
  dt000 [ , recoveryRate:= as.integer(recoveredTotal / confirmedTotal * 100 )]
  dt000 [ , activeTotal.:= confirmedTotal - recoveredTotal - deathTotal]
  
  #   #from us.Rmd: deaths -. death
  # dt[, deathRate := round (death/confirmed*100,2)]
  # dt[, deathRateAverage := round (deathTotal/confirmedTotal*100,2)]
  
  # dt000[order(get(input$sortby))]
  
  dt000 <- covid.reduceToTopNCitiesToday(dt000, input$showN, input$sortby)
  
  # showN = 12
  # showN <- input$showN
  # # if ( showN > 0 )
  # #   dt000 <- dt000 %>% covid.reduceToTopNCitiesToday(showN);dt000 
  # 
  # 
  # # dateMax <- dt0$date %>% max
  # dt <- dt000[date==dateMax][order(-get(input$sortby))][1: min(showN, nrow(dt000))];
  # dt
  # topNcities <- dt$city ; 
  # topNcities
  # dt000 <- dt000[ city %in% topNcities];
  dt000
  
  dt000[, label:=  sprintf("Rt: %.2f (%+.2f). New: %.1f (%+.1f)", confirmedGrowth., confirmedGrowth.Accel, confirmedSpeed, confirmedAccel.)  ]
})

# r.dt000cols ----
r.dt000cols  <- reactive({
  
  
  dt <- r.dt000() [date==dateMax |    date==dateMax-1 |    date==dateMax-7 |  date==dateMax-30 ]  [
    , .(
      # region, 
      date,
      state,
      city,
      confirmedSpeed, confirmedAccel., confirmedGrowth., 
      deathSpeed,
      confirmedTotal,       # activeTotal, 
      # recoveredTotal,
      deathTotal, round(deathTotal/confirmedTotal*100, 2)
      # deathRate
    )] [
      order(state, city, -date)
      # order(region)
    ]
  
  dt[, date:=as.character(date)]
  setnames(dt, c("date" ,	"Province", "Region",	"Confirmed/day" 	,"Acceleration", 	"Growth (Rt)", 	
                 "Deaths/day",
                 "All Confirmed" ,"All Deaths", "Mortality rate (%)")) 
  #TODO change names cols
  
  
  
})



```

```{r r.dt00, include = F}

# See in select

```


## Row ----------- {data-height=1000 .tabset .tabset-fade }



<!-- ### Situation Today {data-height=1000} -->

### Spread & Acceleration 
```{r}
r.gToday <-  reactive({
  dt00 <- r.dt000()
  plotToday2(dt00,input)
  
})
renderPlot( {
  print( r.gToday() )
})

```

### Growth Rate (Rt) 
```{r}
r.gTodayR <- reactive({
  dt00 <- r.dt000()
  plotTodayRt2(dt00,input)
})
renderPlot( {
  print( r.gTodayR() )
})

```

<!-- ### Combined view -->
<!-- <!-- ### Today: `r format(Sys.time(), '%d %B, %Y')` --> -->

<!-- ```{r} -->

<!-- renderPlot( { -->
<!--   plotTodayAll( r.dt000(), input) -->
<!-- }) -->

<!-- ``` -->


# Trends

## Row ----------- 
<!-- ### Pandemic spread analysis -->
<!-- ### Dynamics & Trends -->

### Dynamics over time {data-width=900}

```{r}

r.g <-  reactive({
  
  cols <- c("confirmed", "recovered", "deaths", "active")
  
  cols3 <- paste0(cols, input$fRadio)
  
  # if (input$sortby == "region") {
  #   cols3 <- "confirmedSpeed" 
  # } else {
  #   cols3 <- input$sortby
  # }
  
  
  
  # dt00 <- dt000
  # dt00 <<- r.dt00()[confirmed>0][date>ymd("2020-03-10")]
  dt00 <<- r.dt000()
  
  
  
  # setcolorder(dt00, "date")
  
  # 
  # if (input$normalize == T)
  #   dt00[ , (cols3):= lapply(.SD, function(x) {as.integer(x/population*1000000)}),.SDcols=cols3]
  # 
  
  if (  dt00$region %>% unique %>% length > 0 & dt00 %>% nrow > 0) {
    g <- ggplot( dt00  ) +

      # scale_y_continuous(limits = c(0.5, NA)) +
      scale_y_continuous(limits = c(min(dt00[[ cols3[1] ]]), NA )) +
      
      
      scale_x_date(
        # limits = c( NA, as.Date(dateMax + 3 )),  
        
        date_breaks = "1 week",
        # date_minor_breaks = "1 day", 
        date_labels = "%b %d") +
      
      
      geom_vline(xintercept=dateMax, col = "orange", size=2) +
      geom_vline(xintercept=dateMax-14, col = "orange", size=1) +
      geom_point(aes_string("date", cols3[1]), alpha=0.5, col="purple", size=2) +
      geom_line(aes_string("date", cols3[1]), alpha=0.5, col="purple", size=1) +
      
      
      
      theme_bw() +
      
      labs(
        
        title= paste0("Pandemic dynamics and trends (Last updated ", dateMax, ")"),
        # title= paste0("Pandemic situation today (Last updated ", dateMax, ")"),
        caption=paste0(
          # "Vertical yellow lines indicate two week period. Dash line shows the model of the spread. Grey area indicated 95% confidence interval of the model.\n", 
          # "Data sources: University of Toronto Coronavirus database, Open Government - Canada\n", 
          caption.covid
        ),
        x=NULL,
        y=NULL
        # y=paste(input$sortby)
      )
    
        
    if (input$sortby == "region")  {
      g <- g +  facet_wrap(.~  region,  scales=ifelse(input$scale, "fixed", "free_y")   )
    } else {
      g <- g +  facet_wrap(.~ reorder(region, -get(input$sortby)),  scales=ifelse(input$scale, "fixed", "free_y")   )
    }
    
    if (input$log10 ) {
      g <- g + scale_y_log10()
    }
    
    if (input$fRadio == "confirmedGrowth.") {
      g <- g +  
        geom_hline(yintercept=1, col = "black", size=1, alpha=0.5)  +
        scale_y_continuous(limits = c(0, 2)) 
    }
    
    
    if (input$trend ) {
      
      # if (input$trend_SE ) {
      g <- g + geom_smooth(aes_string("date", cols3[1]), size = 1, level=0.99,
                           method= "gam", # method= "gam",  formula = y ~ s(x,k=3),
                           # method = "lm", formula = y ~ poly(x, 4),
                           col = "black", linetype = 2, alpha=0.5) +
        labs(
          x="Dash line shows the model of the pandemic spread. Grey area indicates 95% confidence interval of the model."
        )
      # } 
    } else {
      g <- g
      # g <- g + geom_smooth(aes_string("date", cols3[1]), size = 1, se = FALSE,
      #                      method= "gam",   # method= "gam",  formula = y ~ s(x,k=3),
      #                      # method = "lm", formula = y ~ poly(x, 4),
      #                      col = "black", linetype = 3, alpha=0.5)
    }
    
  }    else {
    
    g <- ggplot () +  theme_bw() +
      
      annotate("text", x = 1, y = 3, label=paste0(
        "While data is being loaded ... \n\n", 
        "Tip of the Day: \n Bookmark this page on your phone to have LIVE pandemic update in your pocket.\n\n"
        # ,
        # "Quote of the day: \n 'Happiness is not something ready made. It comes from your own actions' (Dalai Lama)"
      ) ) +
      annotate("text", x = 1, y = 1, label="") + 
      annotate("text", x = 1, y = 4, label="") + 
      labs(x=NULL, y=NULL)
    
  }
  
  
})

renderPlot( {
  print( r.g() )
})


```


### Plot settings {data-width=120}


```{r}
radioButtons("fRadio",
             # "Metric to plot:",
             "Show: ", # Metric Functional:", # "f", "Functionals:", Show Compute
             c(
               "Totals" = "Total",
               "Raw daily records" = "",
               "Speed"  = "Speed",
               "Acceleration" = "Accel.",
               # "Growth: N/N'" = "Growth0",
               "Growth rate (Rt)" = "Growth."
               # # "Raw data (records each day, can be noisy): Nraw" = "",
               # "Total infected: N(t) " = "Total",
               # "Speed (average new cases a day): N'(t) "  = "Speed",
               # "Acceleration (average change in speed): N'' " = "Accel.",
               # # "Growth: N/N'" = "Growth0",
               # "Growth rate (a.k.a. Reproduction rate): R(t) = N'(t) / N'(t-1)" = "Growth."               
             ), 
             inline=F,
             selected = "Speed"
)

hr()

# checkboxInput("normalize", "Normalize (per Million)", T)
checkboxInput("scale", "Keep the same scale", F)


checkboxInput("log10", "Use Log scale", F)


checkboxInput("trend", "Overlay model", T)
# checkboxInput("predict", "Show predictions (COMING SOON)", F)




# 
# ```
# 
# ### Processing settings
# 



sliderInput("convolution", 
            # "Adjust precision:", #"Convolution filter size", # "Compute over:", 
            h5("Averaging  window:"), #Precision
            min = 2, max = 10, post  = " days",
            value = 5)



dateInput("dateToday",
          label = "Change date:", weekstart=1,
          # min = dateMax %>% ymd() - 180, #"2020-03-01",
          max = dateToday,
          value = dateMax
)


sliderInput("daysToTrack", label = "Weeks to track:",
            min = 1, max = 30, value=5)



# .................................... -------------

```




# Tables
<!-- # Details -->

## Row ----------- {data-height=1000 .tabset .tabset-fade }

### Today vs. 1/7/30 Days Ago 


```{r}

DT::renderDataTable({

  DT::datatable( r.dt000cols(),
                 filter ="top",
                 rownames = F, 
                 # colnames = c("Country", "Confirmed", "Recovered", "Death"),
                 # colnames = c("region" ,	"date" ,		"Speed (cases/day)" 	,"Acceleration (speed change)", 	"Growth (Rt)", 	"Total confirmed" , "Total active" 	,"Total deaths") ,
                 extensions = c('Buttons','FixedColumns','Scroller'),
                 options = list(dom = 'Blfrtip',
                                scrollX = TRUE,
                                fixedColumns = list(leftColumns = 4, rightColumns = 1),
                                
                                deferRender = TRUE,
                                scrollY = 500,
                                scroller = TRUE,
                                
                                buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                                lengthMenu = list(c(10,25,50,-1),
                                                  c(10,25,50,"All")
                                )
                                )
                 )

  #                options = list(
  # 
  #                  searchHighlight = TRUE,
  #                  scrollX = TRUE,
  #                  #scrollX='400px',
  #                  scrollY = TRUE,
  #                  bPaginate = T,
  #                  pageLength = 10)
  # )
})
```

### Simplified view

```{r}
# 
# renderUI({
#   if (input$tableForPasting) {
#     
renderTable({
  r.dt000cols() 
})


#   } else {
#     renderTable({
#       r.dt000cols() 
#     })
#     
#   }
# })


# checkboxInput("tableForPasting",
#               "Re-format table for pasting", F)


```


### Text only view
<!-- ###  Alternative view -->

```{r}
renderPrint({
  r.dt000cols() %>% knitr::kable()
})



```


###  Interactive table



<!-- # Interactive view -->


<!-- ## ........ {data-height=1000 .tabset .tabset-fade } -->



<!-- ### Dynamics & Trends -->

<!-- ```{r} -->
<!-- renderPlotly( { -->
<!--   ggplotly(r.g()) -->
<!-- }) -->

<!-- ``` -->

<!-- ###  Spread and Acceleration  -->

<!-- ```{r} -->
<!-- renderPlotly( { -->
<!--   ggplotly(r.gToday()) -->
<!-- }) -->


<!-- ``` -->


<!-- ### Growth Rate (Rt) -->

<!-- ```{r} -->
<!-- renderPlotly( { -->
<!--   ggplotly(r.gTodayR()) -->
<!-- }) -->

<!-- # .................................... ------------- -->

<!-- ``` -->



<!-- <!-- ## .... Upper Row {data-height=830 .tabset .tabset-fade } --> -->
<!-- ## .... Upper Row 250 {data-height=400 .tabset .tabset-fade } -->

<!-- ``` -->

<!-- # Report  -->

<!-- ## ............................ -->



<!-- <!-- ## Page 2 {data-orientation=rows} --> -->

<!-- ### Generated by [iTrack](https://itrack.shinyapps.io/PSES) on `r format(Sys.time(), "%d %B, %Y")`.   -->


<!-- **Abstract: ** -->

<!-- The following report is generated automatically from [dataset]() .  -->
<!-- It identifies the areas of highest pandemic Growth, Spread and Acceleration in Canada. -->

<!-- <!-- The results are sorted by Province and by metrics --> -->

<!-- --- -->

<!-- #### National view -->


<!-- --- -->

<!-- #### By Province -->



<!-- ```{r results='asis', fig.width=10, fig.height=2, fig.align='center'} -->
<!--   for (wloc in dtWLOC[Vendor == vendor]$WLOC %>% unique) { -->

<!--     city <- dtWLOC[WLOC==wloc, City] -->

<!--     DIV_START(city) -->

<!--     rmd.cat(glue::glue("\n\n## {city} ({wloc})\n\n")) -->

<!--     dt0 <- dt %>% pik.4city(city) -->

<!--     #pik.plot5numbers(dt0) -->

<!--     # *over time:* ----- -->

<!--     # rmd.cat("\n\n**Performance over time:**\n\n \n\n TBD ") -->
<!--     #  -->
<!--     #  -->
<!--     # rmd.cat("\n\n**Performance by kiosk:**\n\n \n\n TBD ") -->
<!--     #  -->

<!--     DIV_END() -->

<!--   } -->


<!-- ``` -->


<!-- # Settings -->

<!-- ## ............................ -->

<!-- ### Search criteria -->


<!-- ### Display settings -->

```{r}



# 
# renderUI({
#   sliderInput("showN", 
#               h5(paste0( "Limit number of search results (out of ", r.dt00()$city %>% unique %>% length), ")" ),
#               min = 1, max = r.dt00()$city %>% unique %>% length, 
#               # width="100%",
#               step = 1,
#               # post  = " regions",
#               # post  = " most infected regions",
#               # value = min (r.dt00()$city %>% unique %>% length, 12))
#                 value = r.dt00()$city %>% unique %>% length)
# })




# .................................... -------------

```


```{r covid.9.help.Rmd, child = 'covid.9.help.Rmd'}
```

