
<!-- #  Dynamics today (`r format(Sys.time(), '%d %B, %Y')`) -->
<!-- # Daily summary -->
# Search Criteria
<!-- # Today -->

<!-- #### Plot settings: -->
<!-- ```{r} -->
<!-- checkboxInput("log10", "Use Log scale", F) -->
<!-- ``` -->

## .... Upper Row {.tabset .tabset-fade }

<!-- ### COVID-19 dynamics today: speed and acceleration of the pandemic spread -->
<!-- ### COVID-19 dynamics today -->
<!-- ### Dynamics today -->

### Daily summary
<!-- ###  Search results -->

```{r}

# <!-- # Situation on `r paste0(wday(ymd(dateMax), label = TRUE, abbr = FALSE), "," format(dateMax, '%d %B, %Y')`)` -->
r.gToday <-  reactive({
  
  # dt <- r.dtToday()
  
  dt <- r.dt()
 
  
  if ( is.null(input$region)) {
    g <- gQuote
  } else {
    # if (  dt$region %>% unique %>% length > 0) {
    g <- plotToday(dt, input)
  }  

  g
})



renderPlot( {
  print( r.gToday() )
})


```




<!-- >  Number of infected and deaths per day on ", input$dateToday), -->
<!--         # title= paste0("Speed and acceleration of pandemic on ", format(Sys.time(), "%d %B, %Y") ), -->
<!--         # title= paste0("Pandemic dynamics on ", input$dateToday), # dateMax), -->
<!--         subtitle= paste0("Top ", input$showN, " regions ", -->
<!--                          "in ", my.paste(input$country, ", "), " (sorted by '", input$sortby, "')."  -->
<!--                          # , ". States/Provinces: ", my.paste(input$state, ", ")  -->
> The plot shows the speed (new cases per day) and acceleration (daily change in speed) in the number of infected (orange) and the number of deaths (red) for the top found results, sorted according to the selected criteria. Change in the number of infected cases since yesterday is marked by arrow.



###  Clickable graph
<!-- ###Explore search results -->

```{r}

renderPlotly( {
  ggplotly(r.gToday())
})


```

> The plot shows the speed (new cases per day) and acceleration (daily change in speed) in the number o infected (orange) and the number of deaths (red) for the top found results, sorted according to the selected criteria. Change in the number of infected cases since yesterday is marked by arrow.


