---
title: "iTrack Covid"
date: "(`r format(Sys.time(), '%d %B, %Y')`)"
# author: Dmitry Gorodnichy
output: 
  flexdashboard::flex_dashboard:
    # theme: simplex # journal # theme: simplex
    orientation: rows
    social: menu
    # source_code: embed
    vertical_layout: fill #scroll #fill
runtime: shiny       
---


```{r readCov, include=F}
# setwd("/home/dmitry/GitHub/iTrack-covid-priv")
source("covid-read.R")

colsGeo <- c("country",   "state",       "city")
colsCases <- c("confirmed", "deaths", "recovered")

dtGeo <- readRDS("dtGeoAll-0.Rds") 

dtGeo[, (colsGeo):=lapply(.SD, iconv, to="ASCII//TRANSLIT"), .SDcols=colsGeo]
# dtGeo[ , region:=paste0( str_trunc(country, 2, ellipsis = ""), "-", abbreviate(state, 2), ": ",  city)]
# dtGeo[ , region:=paste0( country, "-", state,  ": ",  city)]

# saveRDS(dtGeo, "dtGeoAll-0.Rds")  
# 
dtGeo[, region:=as.ordered(region)]


# # dtGeo[country=="Canada", region:=paste0( abbreviate(state, 3, F), ": ",  city)]
# dtGeo[ , region:=paste0( country, "-", state)]
# dtGeo[country=="Canada", region:=paste0(state, ": ",  city)]
# dtGeo[country=="US", region:=paste0( abbreviate(state, 2), ": ",  city)]



dtJHU <-readCovidJHU() %T>% print; 
dtCa <- readCovidUofT() %T>% print 
dtUS <- readCovidUS() %T>% print


dateMaxCa <- dtUS$date %>% max  (na.rm=T)%>% ymd; dateMaxCa
dateMaxJHU <- dtJHU$date %>% max (na.rm=T)%>% ymd; dateMaxJHU
dateMaxUS<- dtUS$date %>% max (na.rm=T) %>% ymd; dateMaxUS

dtAll <-   dtJHU %>% rbind ( dtCa ) %>% rbind (dtUS)

dtAll [, (colsCases):= lapply(.SD, tidyr::replace_na, 0), .SDcol = colsCases]


dateMax <- min(dateMaxCa, dateMaxUS, dateMaxJHU); dateMax
dateToday <- format(Sys.time(), '%d %B, %Y') %>% dmy

# rm(dtJHU); rm(dtCa); rm(dtUS)



```


<!-- ```{r covid.0.selection.Rmd, child = 'covid.0.selection.Rmd '} -->
<!-- ``` -->


# Search options: {.sidebar}



<!-- #### Define search criteria: -->

```{r searchMenu}


radioButtons("sortby", 
             # h4("Sort results by:"),
             # h4("Search and sort by:"),
             h4("Search / Sort by:"),
             choices=c(
               "Name" = "region",
               "Latitude* " = "lat",
               "Longitude* " = "lng",
               
               "Total infected" = "confirmedTotal",
               ".. per Million*" = "confirmedTotalPerMil",
               # "Density* of cases (Total/Mil)" = "confirmedTotalPerMil",
               "Total deaths" = "deathsTotal",
               ".. per Million*" = "deathsTotalPerMil",
               
               
               # "Infection spread speed" = "confirmedSpeed",
               # "Infection spread growth" = "confirmedGrowth.",
               "Infected per day" = "confirmedSpeed",
               ".. change since yesterday" = "confirmedAccel.",
               "Infected per day growth" = "confirmedGrowth.",
               ".. change since yesterday" = "confirmedGrowth.Accel.",
               
               # "(Deaths per Million*)" = "deathsTotalPerMil",
               
               # "Deaths per Day increase" = "deathsAccel.",
               # "Deaths per Day growth" = "deathsGrowth.",
               "Deaths per day" = "deathsSpeed",
               ".. change since yesterday" = "deathsAccel.",
               "Deaths per day growth" = "deathsGrowth.",
               ".. change since yesterday" = "deathsGrowth.Accel",
               "Mortality rate" = "deathRate"
               
             ),
             selected = "confirmedSpeed",
             inline=F)
# h6("* where population information is available")
# h6("* where information is provided")
h6("* where information is available")

# 
# 
# radioButtons("order.regions", h5("Rearrange menus by:"),
#              choices=c(
#              #  "Latitude " = "lat",
#                "Longitude " = "lng",
#                "Name" = "region",
#              #  "Population*" = "population",
#                "Number of cases" = "confirmedTotal"
#              #  "Mortality rate" = "deathRate"
#              ),
#              selected = "lng",
#              inline=T)
# 




renderUI({
  selectInput('country',
              # h5(paste0 ("Country (out of ", dtAll$country %>% unique %>% length, "):") ),
              h5(paste0 ("Add Country (Press DEL to delete):")),
              multiple=T,
              
              selected = c("Canada"),
              # selected = c("Canada", "US"),
              # selected = STR_ALL,
              choices = c(STR_ALL, dtGeo[state==STR_TOTAL][order(ifelse(input$ascending, 1, -1)*get(input$sortby))]$country %>% unique)
              # choices = c( dtGeo[order(get(input$order.regions))]$country %>% unique)
  )
  
})


renderUI({
  selectInput('state',
              # paste0 ("Select Provinces (out of ", r.dt0()$state %>% unique %>% length - 1, "):"),
              h5(paste0 ("Add State / Province:")),
              multiple=T, 
              #selected = c("Ontario"),
              selected = STR_ALL,
              # selected = c("Ontario", "Quebec", "New York"),
              choices = c(STR_ALL, r.dt0()[order(ifelse(input$ascending, 1, -1)*get(input$sortby))]$state %>% unique  )
  )
})

renderUI({
  selectInput(
    'city',
    h5(paste0 ("Add City / Health Region:") ),
    
    # h5(paste0 ("Add City /Health Regions (out of ", r.dt00()$city %>% unique %>% length - 1, "):") ),
    multiple=T,
    #selected= c("Toronto","Montreal", "New York"),
    selected = STR_ALL,
    choices = c(STR_ALL,  r.dt00()[order(ifelse(input$ascending, 1, -1)*get(input$sortby))]$city %>% unique  )
  )
})


checkboxInput("provincial", h5("Include national aggregates"), F)

checkboxInput("ascending", h5("Change sorting order"), F)



sliderInput("showN",
            # h4("Choose number of results: "),
            # h4("Narrow output to:"),
            # h4("Define Output:"),
            # h4("Limit number of results to:"),
            h4("Change number of results:"),
            # "Find top:",
            min = 1, max = 0, #dtGeo$country%>% unique %>% length/2,
            pre  = "top ",
            post  = " regions",
            # post  = " results",
            value = 10)

dateInput("dateToday",
          label = h4("Change date:"), weekstart=1,
          min = dateMax %>% ymd() - 30, #"2020-03-01",
          max = dateToday,
          value = dateMax
)



```


```{r r.dt000 r.dt r.dtToday, include=F }


r.dt0  <- reactive({
  # #dtGeo
  # dtGeo[ country %in% input$country]
  if (STR_ALL == input$country & length(input$country) == 1 )
    dtGeo
  else
    dtGeo[ country %in% input$country ]
})

r.dt00  <- reactive({
  # r.dt0()[ state %in% input$state ]
  if (STR_ALL == input$state & length(input$state) == 1 )
    r.dt0()
  else
    r.dt0()[ state %in% input$state ]
  
})

r.dt000  <- reactive({
  # if (STR_ALL %in% input$city )
  if (STR_ALL == input$city & length(input$city) == 1 )
    dtGeo <- r.dt00()
  else
    dtGeo <- r.dt00()[ city %in% input$city ]
  # dtGeo <- r.dt00()[ region %in% input$city ]
  
  
  
  if (!input$provincial)
    # dtGeo <- dtGeo[city!=STR_TOTAL | state !=STR_TOTAL ]
    dtGeo <- dtGeo[city!=STR_TOTAL ]
  
  dtGeo <- dtGeo[ , c(colsGeo, "lat", "lng", "population", "region"), with=F]
  dtGeo
})

# dtAll [ dtGeo000 ]  ----



r.dt  <- reactive({
  
  # if (input$country == 'Canada')
  #   dt <- dtCa[ r.dt000(), on =colsGeo]
  # else if (input$country == 'US')
  #   dt <- dtUS[ r.dt000(), on =colsGeo]
  # else 
  #   dt <- dtJHU[ r.dt000(), on =colsGeo]
  
  dtGeo000 <- r.dt000()
  # dtGeo000 <- dtGeo[ country %in% input$country &  state %in% input$state &  city %in% input$city ]
  #   dtGeo000 <- dtGeo[ country %in% input$country &  state %in% input$state ]
  #     dtGeo000 <- dtGeo[ country %in% input$country  ]
  
  dtGeo000 <-    dtGeo000[, c (colsGeo, "lat", "lng", "population", "region"), with=F]
  dtGeo000
  
  dt <- dtAll [dtGeo000, on =c (colsGeo)];dt
  
  dt <- addDerivatives(dt, colsCases, colsGeo, input$convolution)
  dt
  
  
  # Today -----[ [date == input$dateToday] 
  
  dtN <- dt[date==input$dateToday] [order(-get(input$sortby))] [1:input$showN]; dtN
  dtN <- dtN[!is.na(region)]
  
  aRegions <- dtN$region
  dt <- dt[region %in% aRegions]
  
  dt [ , deathRate:= as.integer(deathsTotal / confirmedTotal * 100 )]
  dt [ , recoveryRate:= as.integer(recoveredTotal / confirmedTotal * 100 )]
  dt [ , activeTotal := confirmedTotal - recoveredTotal - deathsTotal]
  
  cols <- c("confirmed", "deaths",  "confirmedTotal" ,  "deathsTotal"  ,  "confirmedSpeed"  , "deathsSpeed"   )
  colsPerMil <- paste0(cols, "PerMil")
  
  dt[ , (colsPerMil):= lapply(.SD, 
                              function(x) {
                                as.integer(x/population*1000000)
                              }),
      .SDcols=cols]
  
  dt
})


r.dtToday  <- reactive({
  
  dtToday <-  r.dt()[date == input$dateToday]
  
  # dateMax <- dt$date %>% max (na.rm=T)
  
  # col <- c("date" ,"state" , "city" ,     
  #          "deathRate"  ,
  #          "confirmedTotal"   , "deathsTotal",       "recoveredTotal", 
  #          "confirmed" ,"deaths"    , "recovered", 
  #          "confirmedSpeed"  ,     "deathsSpeed"    ,    
  #          "confirmedAccel."  ,    "deathsAccel."  ,    
  #          "confirmedGrowth."   ,  "deathsGrowth."   ,     
  #          "confirmedTotalPerMil" ,"deathsTotalPerMil"   , 
  #          "confirmedSpeedPerMil", "deathsSpeedPerMil", "region")
  # 
  # dtToday <- dt[date==dateMax, col, with=F]
  
  # dtToday <-  dtToday[ , region:=reorder(region, get(input$sortby))] [1:input$showN]
  # 
  # # dtToday <- dtToday[ , region:=reorder(region, ifelse(input$ascending, 1, -1)*get(input$sortby))] [1:input$showN]
  # 
  # dt <- dtAll [ dtToday[ , c(colsGeo, "lat", "lng", "population", "region"), with=F], on =colsGeo]
  
  
  
  
  
  # dtToday  [     , .(region, date,
  #       deathsTotal, deathsSpeed, deathRate,
  #       confirmedTotal, confirmedSpeed, confirmedAccel., confirmedGrowth.,
  #       recoveredTotal, activeTotal
  #       # ,
  #       # confirmedAccel, confirmedGrowth
  #   )]
})



```


<!-- # Detect high-risk regions -->
<!-- # Analyze current situation -->
<!-- # Predict dynamics -->
<!-- # Analyze dynamics -->
<!-- # Generate Report -->

#  Dynamics Today
<!-- # Daily summary -->
<!-- # Daily summary-->


<!-- # Condu -->
<!-- # Summary -->


##### Data for US and International are loaded from [JHU Database](https://coronavirus.jhu.edu/map.html) (last updated on `r dtJHU$date %>% max`). Data for Canada are loaded from [UofT Database](https://art-bd.shinyapps.io/covid19canada/) (last updated on `r dtCa$date %>% max ` ). To reload data, press [here](https://itrack.shinyapps.io/covid/).


## .... Upper Row {.tabset .tabset-fade }


### Printable graph
<!-- ###  Search results -->

```{r}

# <!-- # Situation on `r paste0(wday(ymd(dateMax), label = TRUE, abbr = FALSE), "," format(dateMax, '%d %B, %Y')`)` -->
r.gToday <-  reactive({
  
  
  # dt <- r.dtToday()
  
  dt00 <<- r.dt()
  dt <- dt00[date==input$dateToday]
  
  dt <-  dt[ , region:=reorder(region, get(input$sortby))] [ order(-region)][1:input$showN]
  
  
  # cols <- c("confirmed", "recovered", "deaths")
  # cols3 <- paste0(cols, input$fRadio)
  # cols3[1])  
  
  dateMax <- dt$date %>% max (na.rm = T)
  
  g <- dt %>% 
    ggplot(
      # aes(x=region)
      aes(x=reorder(region, get(input$sortby)) )
    )  + 
    theme_bw() +
    # facet_grid(reorder(region, region)~.) +
    
    coord_flip() + # facet_grid( . ~ date) +
    # scale_colour_brewer(palette = "Greens", direction = 1) +   #scale_fill_grey(0.3, 0.9) +
    
    geom_col(aes(y=confirmedSpeed ), alpha=0.2, fill="orange") +
    geom_point(aes(y=confirmedSpeed, size=confirmedTotal ), alpha=0.9, col="orange") +
    geom_point(aes(y=confirmedSpeed-confirmedAccel., size=confirmedTotal-confirmedSpeed ), alpha=0.4, col="orange") + 
    geom_point(aes(y=confirmedSpeed-confirmedAccel., size=confirmedTotal-confirmedSpeed ), alpha=0.4, col="orange") + 
    
    # geom_point(aes_string(y="recovered", size=as.character("date")), alpha=0.8, col="green", fill= "green") +
    # 
    geom_col(aes(y=deathsSpeed), alpha=0.2, fill="red") +
    geom_point(aes(y=deathsSpeed, size=deathsTotal ), alpha=0.9, col="red") +
    geom_point(aes(y=deathsSpeed-deathsAccel., size=deathsTotal-deathsSpeed), alpha=0.4, col="red") +
    
    
    geom_segment( aes( xend=reorder(region, get(input$sortby)),
                       yend=confirmedSpeed, y=confirmedSpeed-confirmedAccel.
    ), 
    size = 1, col="black",
    arrow = arrow(length = unit(0.1, "cm"))
    ) +
    
    guides(fill="none", col="none") +
    # scale_y_log10() +
    
    theme(legend.position = "bottom") +
    labs(
      # title= paste0("Number of infected and deaths per day: today vs. yesterday)"),
      # title= paste0("Speed and acceleration of pandemic on ", format(Sys.time(), "%d %B, %Y") ),
      title= paste0("Pandemic dynamics on ", input$dateToday), # dateMax),
      subtitle= paste0("Top ", input$showN, " regions (sorted by '", input$sortby, "'). ",
                       "Countries: ", my.paste(input$country, ", ") , ". States/Provinces: ", my.paste(input$state, ", ") ),
      # subtitle=paste0(my.paste(input$country, ", ") , " - ", my.paste(input$state, ", ") 
      #                 ), 
      #                 # ". Top: ",
      #                 # min( input$showN,  dt$regions %>% unique %>% length), " regions"),
      
      size="Total number of cases",
      y="Number of infected (orange) and deaths (red) per day. Change since yesterday is marked by arrow.",
      y=NULL,
      x=NULL,
      
      caption=paste0("Generated on ",  format(Sys.time(), "%d %B, %Y") ," by iTrack Covid (https://itrack.shinyapps.io/covid)")
    )
  
  g
})


renderPlot( {
  print( r.gToday() )
})
```



###  Interactive graph
<!-- ###Explore search results -->

```{r}

renderPlotly( {
  ggplotly(r.gToday())
})


```



<!-- ### Printable table -->

<!-- ```{r} -->

<!-- renderTable({ -->
<!--   # col <- c("date" ,"state" , "city" ,      -->
<!--   #          "deathRate"  , -->
<!--   #          "confirmedTotal"   , "deathsTotal",       "recoveredTotal",  -->
<!--   #          "confirmed" ,"deaths"    , "recovered",  -->
<!--   #          "confirmedSpeed"  ,     "deathsSpeed"    ,     -->
<!--   #          "confirmedAccel."  ,    "deathsAccel."  ,     -->
<!--   #          "confirmedGrowth."   ,  "deathsGrowth."   ,      -->
<!--   #          "confirmedTotalPerMil" ,"deathsTotalPerMil"   ,  -->
<!--   #          "confirmedSpeedPerMil", "deathsSpeedPerMil") -->
<!--   # r.dt()[ date == dateMax | date == dateMax-1 | date == dateMax-7, col, with=F]   -->
<!--   # r.dt()[ date == dateMax | date == dateMax-1 | date == dateMax-7, -(8:11,)]   -->
<!--   # r.dtToday() -->
<!--   r.dt()[ date == dateMax, -(8:11)]  -->
<!-- }) -->
<!-- ``` -->


<!-- ### Interactive table -->

### Table

```{r}
DT::renderDataTable({
  # r.dtToday()[ date == dateMax | date == dateMax-1 | date == dateMax-7, -(8:11)]   %>% 
  r.dt()[ date == dateMax, -(8:11)]   %>%
    # r.dtToday() %>% 
    DT::datatable( 
      filter ="top",
      options = list(
        scrollY = TRUE,
        scrollX = TRUE,
        bPaginate = T,
        pageLength = 8)
    )
})
```






<!-- ### Printable table (alternative format) -->

<!-- ```{r} -->

<!-- renderPrint({ -->
<!--    r.dt()[ date == dateMax | date == dateMax-1 | date == dateMax-7]  %>%  -->
<!--     knitr::kable() -->
<!-- }) -->
<!-- ``` -->





# Trends for Tomorrow
<!-- # Detailed analysis -->
<!-- # Full dynamics analysis -->


## .... Upper Row {data-height=170}
<!-- data-orientation=rows } -->


### Model attributes {data-width=100}
<!-- ### Dynamics attributes {data-width=100} -->

```{r}


radioButtons("fRadio", "Show: ", # Metric Functional:", # "f", "Functionals:", Show Compute
             c(
               "Raw data (records/day)" = "",
               "Total" = "Total",
               "Speed" = "Speed",
               "Acceleration" = "Accel.",
               "Growth factor" = "Growth"
             ), inline=F,
             selected = "Speed"
)


hr()


checkboxInput("scale", "Keep scale constant", F)



# checkboxInput("flag.risk", "Flag high-risk regions", T)

checkboxInput("normalize", "Normalize* (per Million)", F)
# 
# h6("* where population data available")
h6("(* where population size is known)")



# 
# # checkboxInput("recovered", "Include recovered statistics", F)
# # checkboxInput("deaths", "Include death statistics", F)
# checkboxInput("recovered", "Show recovery rate", F)
# checkboxInput("deaths", "Show death rate", F)

# h4("Step 3: Model and Forecast ")
#
checkboxInput("trend", "Overlay model", T)
# checkboxInput("predict", "Show predictions (COMING SOON)", F)


# sliderInput("convolution", "Adjust model precision:", #"Convolution filter size", # "Compute over:", #Averaging  window size, #Precision
sliderInput("convolution", "Adjust filter:", #"Convolution filter
            min = 3, max = 13, post  = " days",
            value = 7)



dateInput("date",
          label = "Adjust start date:", weekstart=1,
          min = dateMax %>% ymd() - 30, #"2020-03-01",
          max = dateMax,
          value = dateMax - 30 
)




```


<!-- ### Pandemic spread models -->

### Pandemic dynamics models
<!-- ### Pandemic dynamics -->

```{r}

r.gConfirmed <-  reactive({
  
  cols <- c("confirmed", "recovered", "deaths")
  cols3 <- paste0(cols, input$fRadio)
  
  # dt00 <<- r.dt00()[confirmed>0][date>ymd("2020-03-10")]
  dt00 <<- r.dt()
  
  # dt00 <<- r.dt()
  # dt <- dt00[date==input$dateToday]
  # dt <-  dt[ , region:=reorder(region, get(input$sortby))] [ order(-region)][1:input$showN]
  
  
  #  
  #  dtToday <- dt00[date==dt00$date %>% max]
  # regionsRes <- dtToday[ , region:=reorder(region, get(input$sortby))] [1:input$showN]$regions
  # dt00 <- dt00[region %in% regionsRes]
  
  # 
  # # dtToday <- dtToday[ , region:=reorder(region, ifelse(input$ascending, 1, -1)*get(input$sortby))] [1:input$showN]
  # 
  # dt <- dtAll [ dtToday[ , c(colsGeo, "lat", "lng", "population", "region"), with=F], on =colsGeo]
  
  # dt00 [dtToday]
  
  #  setcolorder(dt00, "date")
  
  dt00 <- addDerivatives(dt00, colsCases, colsGeo, input$convolution)
  
  if (input$normalize == T & dt00$population %>% min(na.rm = T) > 1111)
    dt00[ , (cols3):= lapply(.SD, function(x) {as.integer(x/population*1000000)}),.SDcols=cols3]
  
  dt00 <- dt00[date >= input$date]
  
  if (  dt00$region %>% unique %>% length > 0) {
    g <<- ggplot( dt00  ) + 
      
      #facet_grid(reorder(state, Long)~.) +
      #
      facet_wrap(.~
                   #   region,  
                   # reorder(region, get(input$sortby)),
                   reorder(region, ifelse(input$ascending, 1, -1)*get(input$sortby)),
                 scales=ifelse(input$scale, "fixed", "free_y")   
      ) +
      scale_y_continuous(limits = c(0, NA)) +
      geom_vline(xintercept=dateMax, col = "orange", size=2) +
      geom_vline(xintercept=dateMax-14, col = "orange", size=1) +
      geom_point(aes_string("date", cols3[1]), alpha=0.5, col="purple", size=2) +
      geom_line(aes_string("date", cols3[1]), alpha=0.5, col="purple", size=1) +
      
      
      
      theme_bw() +
      scale_x_date(date_breaks = "1 week",
                   date_minor_breaks = "1 day", date_labels = "%b %d") +
      labs(
        #title=paste0("Pandemic situation in ", input$state), # ":   Historical vs. Predicted"),
        title= paste0("Pandemic dynamics: Cases ", input$fRadio, " over time"),
        #  title=paste0("", input$country), # ": Historical vs. Predicted"),
        
        # subtitle= "The number of Confirmed, Recovered, Death cases",
        subtitle=paste0("", my.paste(input$state, ", "), ". Last updated: ", dateMax ), # ": Historical vs. Predicted"),
        #subtitle=paste0("Dates: ", dtJHU$date %>% min, " - ", dtJHU$date %>% max),
        
        caption=paste0("Generated on ",  format(Sys.time(), "%d %B, %Y") ," by iTrack Covid (https://itrack.shinyapps.io/covid)"),
        
        # y=paste("Cases", input$fRadio, ifelse(input$normalize, " (per Million)","")),
        y=paste("Cases"),
        x=NULL
      )
    
    
    if (input$trend ) {
      
      # if (input$trend_SE ) {
      g <- g + geom_smooth(aes_string("date", cols3[1]), size = 1, level=0.99,
                           method= "gam", # method= "gam",  formula = y ~ s(x,k=3),
                           # method = "lm", formula = y ~ poly(x, 4),
                           col = "black", linetype = 3, alpha=0.3)
      # } else
      #   {
      #   g <- g + geom_smooth(aes_string("date", cols3[1]), size = 1, se = FALSE,
      #                        method= "gam",   # method= "gam",  formula = y ~ s(x,k=3),
      #                        # method = "lm", formula = y ~ poly(x, 4),
      #                        col = "black", linetype = 3, alpha=0.5)
      # }
      
    }
  } else {
    
    g <<- ggplot () +  theme_bw() +
      
      # annotate("text", x = 1, y = 2,  label = paste("Thank you for using iTrack Covid App.")    ) +
      # annotate("text", x = 1, y = 4,  label = "Please wait until the App loads the data...") + 
      # annotate("text", x = 1, y = 4,  label = "While data is being loaded from  University of Toronto database ...") + 
      
      annotate("text", x = 1, y = 3, label=paste0(
        "While data is being loaded ... \n\n", 
        "Tip of the Day: \n Bookmark this page on your phone to have live pandemic update in your pocket.\n\n"
        # ,
        # "Quote of the day: \n 'Happiness is not something ready made. It comes from your own actions' (Dalai Lama)"
      ) ) +
      annotate("text", x = 1, y = 1, label="") + 
      annotate("text", x = 1, y = 4, label="") + 
      labs(x=NULL, y=NULL)
    
  }
})

renderPlot( {
  print( r.gConfirmed() )
})
```


<!-- ###  Dynamics (clickable) -->

<!-- ```{r} -->

<!-- renderPlotly( { -->
<!--   ggplotly(r.gConfirmed()) -->
<!-- }) -->


<!-- ``` -->



<!-- # Tables -->

<!-- ## .... Upper Row {.tabset .tabset-fade } -->


<!-- ### r.dt  -->


<!-- ```{r} -->
<!-- DT::renderDataTable({ -->
<!--   DT::datatable( r.dt(), -->
<!--                  filter ="top", -->
<!--                  options = list( -->
<!--                    scrollY = TRUE, -->
<!--                    scrollX = TRUE, -->
<!--                    bPaginate = T, -->
<!--                    pageLength = 8) -->
<!--   ) -->
<!-- }) -->
<!-- ``` -->



<!-- ### dt00 -->


<!-- ```{r} -->
<!-- DT::renderDataTable({ -->
<!--   DT::datatable( r.dt00(),  filter ="top") -->

<!-- }) -->

<!-- ``` -->



<!-- ### dt000 -->


<!-- ```{r} -->
<!-- DT::renderDataTable({ -->
<!--   DT::datatable( r.dt000() ) -->
<!-- }) -->
<!-- ``` -->



<!-- ### dtAll  -->

<!-- ```{r} -->
<!-- DT::renderDataTable({ -->
<!--   DT::datatable( dtAll ,  filter ="top") -->
<!-- }) -->
<!-- ``` -->




<!-- ### dt  -->


<!-- ```{r} -->
<!-- DT::renderDataTable({ -->
<!--   DT::datatable( r.dt() ) -->
<!-- }) -->
<!-- ``` -->

<!-- ### dt000 (renderTable) -->

<!-- ```{r} -->
<!-- renderTable({ -->
<!--   r.dt000()  -->
<!-- }) -->
<!-- ``` -->




<!-- ### dt000 (xtable) -->

<!-- ```{r results='asis'} -->
<!-- renderPrint({ -->
<!--   r.dt000() %>% xtable::xtable (type="html") %>% print -->
<!-- }) -->
<!-- ``` -->




<!-- ### dt000 (stargazer) -->

<!-- ```{r results='asis' } -->
<!-- renderPrint({ -->
<!--   r.dt000() %>% stargazer::stargazer(ype = "html") -->
<!-- }) -->
<!-- ``` -->



<!-- ### dt000 (kable as is print) -->

<!-- ```{r results='asis'} -->
<!-- renderPrint({ -->
<!--   r.dt000() %>% knitr::kable()%>% print -->
<!-- }) -->
<!-- ``` -->



<!-- ### dt000 (kable print) -->

<!-- ```{r } -->
<!-- renderPrint({ -->
<!--   r.dt000() %>% knitr::kable() %>% print -->
<!-- }) -->
<!-- ``` -->



```{r covid.9.help.Rmd, child = 'covid.9.help.Rmd'}
```

